Technologies of Semantic WEB as an environment of application development and integration

### 2021-11-10 paper-aicts-cherkashin.tex
Added an abstract.

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX{} document is presented as an
  article formatted for publication by CEUR-WS in a conference
  proceedings. Based on the ``ceurart'' document class, this article
  presents and explains many of the common variations, as many well as
  of the formatting elements an author may use in the preparation of
  the documentation of their work.
\end{abstract}

@@

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
\end{figure}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Semantic Web technologies and standards are becoming one of productive assets for software development and integration on various levels of design and implementation.  This include OSI level 6 data representation, database and file storage formats, the source data for indexes, hypertext markup, source data for document authoring, representing abstract software models, \emph{etc}.  They also smoothly combined with development and data analysis tools, giving raise a new common-ground environment for realizing integration on the semantic level.

  This paper presents the view on the Semantic Web technologies as data representation for software development tools with model analysis, transformation and retrospection capabilities.  Three examples are presented, exposing our experience.
\end{abstract}

@@

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}
  \centering
  % \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
\end{figure}
